---
title: "Snabb process analysis"
output:
  html_notebook:
    fig_width: 8
    fig_height: 6
---

```{r include=FALSE}
source("vmprofiler.R")
source("latencyr.R")
source("snabbr.R")

set <- read_process_set("data")
```

## Latency

Latency histogram data records the duration of each breath that the engine takes. Every breath is counted into one of ~500 bins corresponding to durations from one microsecond up to one second.

```{r echo=FALSE}
plot_latency_histogram(set$latency.histogram)
```

## VMProfile

VMProfile data records code profiler samples. One sample is taken each microsecond and each sample is counted in a bin keyed by both the class of the app that is currently running and the virtual machine state.

```{r echo=FALSE}
plot_vmprofile(set$vmprofile)
```

States:

- `asm` when the JIT is assembling machine code.
- `c` when running a Lua-C API call (typically into the LuaJIT runtime system.)
- `exit` when a trace exit handler is running.
- `foreign` when running machine code not assembled by the JIT (typically via FFI.)
- `gc` when garbage collecting.
- `interp` when interpreting Lua bytecodes.
- `head` when running JIT machine code that is not part of a trace loop.
- `loop` when running JIT machine code that is part of a trace loop.
- `record` when the JIT is recording a bytecode trace.


## Timeline

### Breaths efficiency

```{r echo=FALSE, message=FALSE}
breath_efficiency(set$breaths)
```

### Callback efficiency

```{r echo=FALSE, message=FALSE}
callback_efficiency(set$callbacks)
```
